---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RuiCountMissing

<!-- badges: start -->

<!-- badges: end -->

The goal of RuiCountMissing is to count missing values in a dataset. This package only includes one function called 'count_all_missing_by_group', which is to count missing values for all columns by group.

## Installation

You can install the development version of RuiCountMissing from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/RuiCountMissing", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(RuiCountMissing)
## basic example code
count_all_missing_by_group(airquality, Month)
```

```{r}
airquality |> count_all_missing_by_group(Month) 
```

```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
