---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RuiCountMissing

<!-- badges: start -->

<!-- badges: end -->

The goal of `RuiCountMissing` is to count missing values in a dataset. This package only includes one function called `count_all_missing_by_group`, which is to count missing values for all columns by group.

## Installation

You can install the development version of `RuiCountMissing` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/RuiCountMissing", ref = "0.1.0")
```

## Examples

### Example1

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column.

```{r example}
library(RuiCountMissing)
count_all_missing_by_group(airquality, Month)
```

### Example2

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function.

```{r}
library(RuiCountMissing)
airquality |> count_all_missing_by_group(Month) 
```

### Example3

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples.

```{r}
library(RuiCountMissing)
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
